---
title: "DS607_Project3_JagdishChhabria"
author: "Jagdish Chhabria"
date: "March 21, 2019"
output: pdf_document
---

## Load required packages and input data
Load the input data file containing the following details of research papers in Artificial Intelligence, Data Science, Machine Learning, Visualization: Names of faculty members who authored these papers, universities they're affiliated to, conferences they presented at, and the year of publication.

```{r}
library(XML)
library(xml2)
library(RCurl)
library(rvest)
library(dplyr)
library(httr)
library(stringr)
library(data.table)

fileurl<-"https://raw.githubusercontent.com/completegraph/DATA607PROJ3/master/Code/author-info-ds.csv"
ds.authors<-read.csv(file=fileurl, header=TRUE, na.strings = "NA", stringsAsFactors = TRUE)
#ds.authors<-fread(fileurl, header=TRUE, na.strings = "NA", stringsAsFactors = FALSE)
#ds.authors

```

## Filter the data for the 2 main columns of interest: University and Adjusted Count
The adjusted count is a score that measures contribution by authors based on joint ownership with other authors. The detailed methodology is available at http://csrankings.org/#/index?all
The analysis below aims to determine which university across the globe, can be deemed to be a thought leader in the Data Science, Artificial Intelligence, Machine Learning and Visualization areas, based on the contribution of their faculty members by writing research papers.

The following section selects the required columns, and calculates an aggregate of the adjusted count by university.Then it renames the columns, and derives the top 10 universities based on this adjusted count metric.

```{r}
paper.count<-ds.authors%>%select(university,adjustedcount)
summary.paper.count<-aggregate(. ~ university, data = paper.count, sum)%>%setorder(-adjustedcount)
summary.paper.count$adjustedcount<-round(summary.paper.count$adjustedcount,2)
colnames(summary.paper.count)<-c("University", "Research_Adj_Count")
#summary.paper.count
top10<-summary.paper.count[1:10,]
top10
#barplot(top10$Research_Adj_Count,horiz=TRUE, axes=TRUE, axisnames=TRUE,names.arg=top10$University ,xlab="University", ylab="Research Paper Count")
```

## Graph the top 10 universities 
The following section generates a barplot showing the top 10 universities by adjusted count. It shows that Carnegie Mellon sits at the top of the stack by a big margin. 

```{r}
library(ggplot2)
library(RColorBrewer)

ggplot(top10, aes(x=University, y=Research_Adj_Count)) +
geom_bar(stat="identity",color="black", fill="blue") + coord_flip() + theme(legend.position='none') + ylab("Research Paper Count") + xlab("Universities")


```

